%-------------------------
% Resume - Soojal Kumar
% One Page Software Engineering Resume
%-------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage[english]{babel}
\usepackage{times}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{array}

\addtolength{\oddsidemargin}{-0.62in}
\addtolength{\textwidth}{1.24in}
\addtolength{\topmargin}{-0.78in}
\addtolength{\textheight}{1.5in}

\linespread{0.98}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\raggedright

\titleformat{\section}
  {\vspace{-7pt}\bfseries\large}
  {}{0em}{}[\titlerule \vspace{-5pt}]

\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=0.16in}

\newcommand{\resumeItem}[1]{\item #1}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4}
  \end{tabular*}
}

\newcommand{\projectHeading}[3]{
  \item
  \begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{#1} & #2 \\
    \textit{#3} &
  \end{tabular*}
}

\begin{document}

%----------HEADER----------
\begin{center}
  {\LARGE \textbf{Soojal Kumar}} \\[-1pt]
  California, United States $|$
  \href{mailto:s_kumar18@u.pacific.edu}{s\_kumar18@u.pacific.edu} $|$
  \href{https://github.com/SoojalKumar}{github.com/SoojalKumar} $|$
  \href{https://linkedin.com/in/soojal-kumar-sk}{linkedin.com/in/soojal-kumar-sk}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\textbf{University of the Pacific}, Stockton, CA \hfill 2021 -- Dec 2025 \\
\textit{Bachelor of Science in Computer Science} \\
Relevant Coursework: Artificial Intelligence, Data Structures, Computer Systems \& Networks, Digital Design, Discrete Math, Programming for Data Science, Application Development

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\textbf{Languages:} Python, TypeScript, JavaScript, Java, C++, PHP, HTML, CSS, SQL \\
\textbf{Frontend/Backend:} React, Next.js, Tailwind CSS, FastAPI, REST APIs, SQLite, API Authentication, Request Validation, Pagination \\
\textbf{AI/Data/Systems:} Machine Learning, NLP, Genetic Algorithms, NumPy, Matplotlib, Linux, Unix, Docker, Git, GitHub Actions, CLI Tools, Speech Recognition

%-----------EXPERIENCE-----------
\section{Experience}
\begin{itemize}

\resumeSubheading
  {Operations Manager Intern}{May 2025 -- Sep 2025}
  {Alaska Car \& RV Rentals}{Anchorage, AK}
\begin{itemize}
  \resumeItem{Managed daily rental operations across reservations, check-ins, agreements, payments, insurance coordination, and customer support workflows.}
  \resumeItem{Streamlined fleet tracking for availability, mileage, damages, service history, cleaning, inspections, and maintenance coordination.}
  \resumeItem{Coordinated between customers, staff, insurers, workshops, and management to reduce operational delays and support high-demand seasonal activity.}
\end{itemize}

\resumeSubheading
  {Deputy Director of Diversity, Equity, and Inclusion}{Nov 2024 -- May 2025}
  {ASUOP, University of the Pacific}{Stockton, CA}
\begin{itemize}
  \resumeItem{Coordinated student government operations with campus organizations, university stakeholders, and student leadership teams.}
  \resumeItem{Improved communication workflows by identifying operational gaps, supporting documentation, and contributing practical recommendations.}
\end{itemize}

\resumeSubheading
  {Teaching Observation Partner}{Dec 2023 -- May 2024}
  {University of the Pacific}{Stockton, CA}
\begin{itemize}
  \resumeItem{Observed classroom dynamics and delivered structured feedback to help faculty improve engagement, learning outcomes, and equity-focused teaching practices.}
\end{itemize}

\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\begin{itemize}

\projectHeading
  {Cloud-Based API Service}{Jan 2026 -- Apr 2026}
  {FastAPI, Python, React, TypeScript, SQLite, Docker, GitHub Actions}
\begin{itemize}
  \resumeItem{Developed a production-style task management API with CRUD operations, API-key authentication, validation, pagination, filtering, health checks, and structured error handling.}
  \resumeItem{Built a React/TypeScript dashboard and Dockerized full-stack workflow to streamline task creation, updates, filtering, deletion, and deployment readiness.}
  \resumeItem{Automated validation through GitHub Actions CI/CD, improving reliability and reducing manual build-check effort before deployment.}
\end{itemize}

\projectHeading
  {EchoWear}{Aug 2025 -- Dec 2025}
  {Mobile Application, Speech Recognition, Haptic Feedback, Accessibility}
\begin{itemize}
  \resumeItem{Designed an accessibility-focused mobile and wearable interaction system using wake-word detection, customizable keywords, and haptic feedback.}
  \resumeItem{Implemented real-time voice-triggered workflows that improved hands-free interaction and reduced reliance on touch-based navigation.}
  \resumeItem{Enhanced user responsiveness through immediate vibration feedback, visual confirmation, and structured keyword management across mobile and smartwatch-style interfaces.}
\end{itemize}

\projectHeading
  {GenAI Project -- Genetic Algorithm Optimization Engine}{Aug 2024 -- Dec 2024}
  {Python, Genetic Algorithms, Optimization, NumPy, Matplotlib}
\begin{itemize}
  \resumeItem{Implemented a genetic algorithm framework using selection, crossover, mutation, and elitism to optimize candidate strategies from historical data.}
  \resumeItem{Designed configurable CLI experiments with training/testing workflows, JSON summaries, and fitness progression plots to improve experiment tracking.}
  \resumeItem{Streamlined performance analysis by generating structured outputs and visualizations for comparing optimization behavior across generations.}
\end{itemize}

\end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------
\section{Certifications \& Awards}
\begin{itemize}
  \resumeItem{\textbf{Best Paper Award}, IJAIBDCMS -- Explainable AI for Intrusion Detection Systems, Apr 2026}
  \resumeItem{\textbf{Docker Essentials: A Developer Introduction}, IBM, Apr 2026}
\end{itemize}

\end{document}
